Evaluate PEER in each cohort and brain region

### 2021-03-11 combined_analysis/eval_resid_in_each.Rmd
add CTS

  nEXP_OBJ = File(file, 
                  name = description, 
                  parentId = CODE$properties$id)
  # synStore(nEXP_OBJ, used = ALL_USED_IDs, executed = thisFile)
}
```

@@

```{r CTS.eval_peer}
# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath,
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath)

@@

    PEER_setNk(model,30)

>>>>

@@

```{r CTS.eval_peer}
# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath + EV.1 + EV.2 + EV.3 + EV.4 + EV.5,
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + EV.1 + EV.2 + EV.3 + EV.4 + EV.5)

@@

    # PEER_setNmax_iterations(model, 2)
    PEER_setNk(model,50)
